5D de-aliased seismic data interpolation using non-stationary prediction error filter

### 2021-10-17 npef/paper.tex
Sun Oct 17 00:57:31 CDT 2021

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_obs5d_new-cog-zA}
   \label{fig:r_obs5da}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_obs5d_new-cog-zB}
   \label{fig:r_npef5db}}\\
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_npef5d_new-cog-zA}
   \label{fig:r_obs5da}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_npef5d_new-cog-zB}
   \label{fig:r_npef5db}}\\
\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:ra_obs5d,ra_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:ra_obs5d,ra_npef5d}.}
\label{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}
\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/os_obs}
%    \label{fig:os_obs}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/os_recon}
%    \label{fig:os_recon}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/ts_recon}
%    \label{fig:ts_recon}}
%	\caption{\new{Comparison between the two-step and one-step interpolation strategies. (a) Observed data when binned onto the regular grids of two times denser. (b) Reconstructed data by the one-step rank-reduction interpolation strategy. (c) Reconstructed data by the two-step rank-reduction and NPEF interpolation strategy.}  }
%	\label{fig:os_obs,os_recon,ts_recon}
%\end{figure}
%
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zero2d}
%    \label{fig:zero2d}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d2}
%    \label{fig:recon2d2}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d}
%    \label{fig:recon2d}}\\
%	\caption{\new{De-aliased interpolation results of the second field data example for a common shot gather. Each gather has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the rank-reduction method completely fails in this case.}}
%	\label{fig:zero2d,recon2d2,recon2d}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zerofk2d}
%    \label{fig:zerofk2d}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d2}
%    \label{fig:reconfk2d2}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d}
%    \label{fig:reconfk2d}}\\
%	\caption{\new{FK spectra of de-aliased interpolation results of the second field data example.  Each gather has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method.}}
%	\label{fig:zerofk2d,reconfk2d2,reconfk2d}
%\end{figure}
}

>>>>

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_obs5d_new-cog-zA}
   \label{fig:r_obs5da}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_obs5d_new-cog-zB}
   \label{fig:r_npef5db}}\\
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_npef5d_new-cog-zA}
   \label{fig:r_obs5da}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_npef5d_new-cog-zB}
   \label{fig:r_npef5db}}\\
\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:ra_obs5d,ra_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:ra_obs5d,ra_npef5d}.}
\label{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}
\end{figure}

%\begin{figure}[htb!]
%   \centering
%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_obs}
%   \label{fig:os_obs}}\\
%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/os_recon}
%   \label{fig:os_recon}}\\
%   \subfloat[]{\includegraphics[width=\textwidth]{real5dos/Fig/ts_recon}
%   \label{fig:ts_recon}}
%\caption{\new{Comparison between the two-step and one-step interpolation strategies. (a) Observed data when binned onto the regular grids of two times denser. (b) Reconstructed data by the one-step rank-reduction interpolation strategy. (c) Reconstructed data by the two-step rank-reduction and NPEF interpolation strategy.}  }
%\label{fig:os_obs,os_recon,ts_recon}
%\end{figure}

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/zero2d}
   \label{fig:zero2d}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/recon2d2}
   \label{fig:recon2d2}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/recon2d}
   \label{fig:recon2d}}\\
\caption{\new{De-aliased interpolation results of the second field data example for a common shot gather. Each gather has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the rank-reduction method completely fails in this case.}}
\label{fig:zero2d,recon2d2,recon2d}
\end{figure}

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/zerofk2d}
   \label{fig:zerofk2d}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/reconfk2d2}
   \label{fig:reconfk2d2}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{real2/Fig/reconfk2d}
   \label{fig:reconfk2d}}\\
\caption{\new{FK spectra of de-aliased interpolation results of the second field data example.  Each gather has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method.}}
\label{fig:zerofk2d,reconfk2d2,reconfk2d}
\end{figure}
}
